Network Configuration Synthesis with Abstract Topologies

### 2016-11-04 paper/abstraction/paper.tex
explain algorithm via example

\begin{figure}
  \begin{center}
    \includegraphics[width=.66\columnwidth]{figures/analysis}
  \end{center}
  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
  \vspace{-1em}
\end{figure}

@@

The abstract disjoint path analysis computes

>>>>

@@

The abstract disjoint path analysis starts from a fixed source location $src$ and repeatedly applies the inference rules from Figure~\ref{fig:inference-rules} until a fixed point is reached. Inference rule conditions are checked for validity over all concrete topologies using the Z3 \ryan{cite} SMT solver. In order to ensure termination, we make the observation that, for any fact learned of the form $L(j,k)$, it is sound to instead infer $L(j',k')$ if $j' \leq j$ and $k' \leq k$. Therefore, for each inference rule that learns a fact of the form $L(j,k)$ we minimize the symbolic expressions for $j$ and $k$ subject to the topology constraints using the Z3 optimizing constraint solver.

\begin{figure}
  \begin{center}
    \includegraphics[width=.66\columnwidth]{figures/analysis}
  \end{center}
  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
  \label{fig:example-inference}
  \vspace{-1em}
\end{figure}

Consider again the datacenter example from \S\ref{sec:overview}. For global prefixes we used the routing policy:
%
\[ \begin{array}{c}
  \$PG \Path end(TG)
\end{array} \]
\noindent
%
Suppose now we additionally add the valleyfree constraint that traffic never has takes a path with a down-up in it. Figure~\ref{fig:example-inference} shows the abstract product graph representation for this routing policy. The inference algorith starts from the node $(TG,0,0)$ with the initial fact $S_P S_{TG}(1,\infty)$
\ryan{todo}
